RNA-seq from 4 cell populations

### 2022-03-30 deconvolution/fans4/molec_profiling.Rmd
update paths

# file_SampleAttributesDS = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt"
file_SampleAttributesDS = synGet('syn22321103')$path

# file_SubjectPhenotypesDS= "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SubjectPhenotypesDS.txt"
file_SubjectPhenotypesDS = synGet('syn22321104')$path

# file_counts = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_reads.gct.gz"
file_counts = synGet('syn22321107')$path

>>>>

file_SampleAttributesDS = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt"
# file_SampleAttributesDS = synGet('syn22321103')$path

file_SubjectPhenotypesDS= "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SubjectPhenotypesDS.txt"
# file_SubjectPhenotypesDS = synGet('syn22321104')$path

file_counts = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_reads.gct.gz"
# file_counts = synGet('syn22321107')$path
